Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-12 paper.tex
Froude number is mentioned later

\todo[inline]{Talk about interdependence of Froude number. What is the Froude
number at 1 m/s?}

@@

Full power and rotor drag (a.k.a. thrust) coefficient curves for various
Reynolds numbers are plotted in Figure~\ref{fig:cp-curves} and
Figure~\ref{fig:cd-curves}, respectively. There is essentially no change in the
shape of the drag coefficient curves---merely an upward shift in $C_D$ with
increasing $Re$.

In general, maximum $C_P$ increases with Reynolds number, which is due to an
increase in the foil lift-to-drag ratio. The power coefficient curves also show
a slight downward shift in the optimal tip speed ratio (peak performance) with
increasing Reynolds number, from about $\lambda \approx$ 2.0 to 1.9. This is
caused by the stall delay from a more turbulent boundary later on the blade
suction side. There is essentially no change in the shape of the drag
coefficient curves---merely an upward shift in $C_D$ with increasing $Re$.

@@

The behavior of the mean rotor drag coefficient is similar, though the changes
are less dramatic. This is likely due to cross-flow turbine geometry, where
increases in blade drag at lower $Re$ somewhat offset the reduction in lift, to
keep total streamwise force from changing as much as the rotor torque. The
tendency for $C_D$ to continue increasing with $Re$ may also be a consequence of
increasing Froude number, which therefore increases free surface deformation and
wave drag during towing without increasing flow through the turbine.

>>>>

@@

Full power and rotor drag (a.k.a. thrust) coefficient curves for various
Reynolds numbers are plotted in Figure~\ref{fig:cp-curves} and
Figure~\ref{fig:cd-curves}, respectively. In general, maximum $C_P$ increases
with Reynolds number, which is due to an increase in the foil lift-to-drag
ratio. The power coefficient curves also show a slight downward shift in the
optimal tip speed ratio (peak performance) with increasing Reynolds number, from
about $\lambda \approx$ 2.0 to 1.9. This is caused by the stall delay from a
more turbulent boundary later on the blade suction side. There is essentially no
change in the shape of the drag coefficient curves---merely an upward shift in
$C_D$ with increasing $Re$.

@@

The behavior of the mean rotor drag coefficient is similar, though the changes
are less dramatic. This is likely due to cross-flow turbine geometry, where
increases in blade drag at lower $Re$ somewhat offsets the reduction in lift, to
keep total streamwise force from changing as much as the rotor torque. The
tendency for $C_D$ to continue increasing with $Re$ may also be a consequence of
increasing Froude number, which therefore increases free surface deformation and
wave drag during towing without increasing flow through the turbine.
